Practical Machine Learning - assignment writeup
========================================================

We will start by loading the caret library, and then reading all data:

```{r}
library(caret)
set.seed(33833)
data <- read.csv("pml-training.csv")
```

Some variables should be excluded because most of them are NA:
```{r}
remove <- apply(data,2,function(x) sum(is.na(x)))
data <- data[,names(remove[remove < 1000])]
```
The total number of remaining variables is `r dim(data)[2]`.
We will then divide this data into training and test sets with 60% of the data in the training set:
```{r}
inTrain <- createDataPartition(y=data$classe,p=0.6,list=FALSE)
training <- data[inTrain,]
testing <- data[-inTrain,]
```

We will use Random Forests prediction alogorithm on the training data set:
```{r}
myctrl <- trainControl(allowParallel=TRUE, method="cv", number=4)
modelFit <- train(classe~.,data=training,model="rf",trControl=myctrl)
```

To test out of sample error we need to predict our model in a new data set (the remaining 40% of observations) as following:
```{r}
pred <- predict(modelFit, testing)
```
We can then assess the accuracy of our model as following:

```{r}
dd <- confusionMatrix(pred,testing$classe)
dd
```

As we can see from the confusion matrix, the overall accuracy for this model is `r as.numeric(dd$overall['Accuracy'])`